Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-29 colt-21/cvx-flats.tex
intro pass

\section{Introduction}\label{sec:intro}
%supervised learning blah
A surrogate loss function is an error measure that one optimizes, that is related but not identical to one's target problem of interest.
Surrogate risk minimization is one of the most widespread techniques in supervised machine learning.
There are two main reasons why a surrogate loss is necessary: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the goal is to estimate some target statistic rather than a target loss, as in many continuous estimation problems.
%(1) often occurs in discrete settings such as classification, while (2) is commone in continuous prediction problems when one seeks to estimate a target conditional statistic.%\raft{I felt we needed a sentence like this to justify \emph{why} we need a surrogate. And given that we need it, we can't really avoid hinting at the quadrants...}
In both settings, one minimally requires \emph{consistency}, a precursor to excess risk bounds and convergence rates.
Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest, i.e. (1) the target risk is also minimized, or (2) the continuous prediction approaches the true conditional statistic.

% examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
Despite the ubiquity of surrogate losses, we lack general frameworks to design and analyze surrogates.
This state of affairs is especially dire when one seeks surrogates with low \emph{prediction dimension}, the dimension of surrogate prediction domain (e.g.\ the number of labels for multiclass classification).
(1) In structured prediction and extreme classification, the prediction dimension can easily become intractably large, and often one sacrifices consistency for lack of better surrogates.
\raf{Expand a bit; we lack tight bounds}
\jessie{Attempt}
Without a general framework for surrogate loss construction and analysis, it is impossible to determine if these sacrifices are necessary, or if there are ways to improve dimensionality without sacrificing consistency.
(2) Risk measures such as conditional value at risk (CVaR) have applications in financial regulation, robust engineering design, and algorithmic fairness, yet provably cannot be given via a target loss.
These applications therefore require a surrogate loss, and preferrably one of low (or at least finite) prediction dimension.
Recent work~\citep{fissler2016higher,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex: bounds for convex surrogates is left as a major open question.

We present a unification of existing techniques to bound the prediction dimension of consistent convex surrogates in both settings above.
In (1), we recover the feasible subspace dimension result of \citet{ramaswamy2016convex}, and give an example where our bound is even tighter.
In (2), we give the first prediction dimension bounds for risk measures with respect to convex surrogates, addressing the open question above.
Our framework rests on property elicitation, a weaker condition than calibration, as a tool to understand consistency across a wide variety of domains.

>>>>

\section{Introduction}\label{sec:intro}
%supervised learning blah
A surrogate loss function is an error measure that that is related but not identical to one's target problem of interest.
Selecting a hypothesis by minimizing surrogate risk is one of the most widespread techniques in supervised machine learning.
There are two main reasons why a surrogate loss is necessary: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the goal is to estimate some target statistic and there is no target loss, as in many continuous estimation problems.
%(1) often occurs in discrete settings such as classification, while (2) is commone in continuous prediction problems when one seeks to estimate a target conditional statistic.%\raft{I felt we needed a sentence like this to justify \emph{why} we need a surrogate. And given that we need it, we can't really avoid hinting at the quadrants...}
In both settings, a key criteria for choosing a surrogate loss is \emph{consistency}, a precursor to excess risk bounds and convergence rates.
Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest, i.e. in (1) the target risk is also minimized, or in (2) the continuous prediction approaches the true conditional statistic.

% examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
Despite the ubiquity of surrogate losses, we lack general frameworks to design and analyze surrogates.
This state of affairs is especially dire when one seeks low \emph{prediction dimension}, the dimension of the surrogate prediction domain.
For example, in multiclass classification with $n$ labels, the prediction domain might be $\reals^n$.
In many type (1) settings, such as structured prediction and extreme classification, the prediction dimension can easily become intractably large, and often one sacrifices consistency for lack of better surrogates.
\raf{Expand a bit; we lack tight bounds}
\jessie{Attempt}
Without a general framework for surrogate loss construction and analysis, it is impossible to determine if these sacrifices are necessary, or if there are ways to improve dimensionality without sacrificing consistency.
Challenges of type (2) include risk measures such as conditional value at risk (CVaR).
These have applications in financial regulation, robust engineering design, and algorithmic fairness, yet provably cannot be specified via a target loss.
These applications therefore require a surrogate loss, and preferrably one of low (or at least finite) prediction dimension.
Recent work~\citep{fissler2016higher,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex: bounds for convex surrogates are a major open question.

We present a unification of existing techniques to bound the prediction dimension of consistent convex surrogates in both settings above.
Applied to settings of type (1), we recover the feasible subspace dimension result of \citet{ramaswamy2016convex}, and give an example where our bound is even tighter.
For type (2), we give the first prediction dimension bounds for risk measures with respect to convex surrogates, addressing the open question above.
Our framework rests on \emph{property elicitation}, a weaker condition than calibration, as a tool to understand consistency across a wide variety of domains.
